Stateless Model Checking with Data-Race Preemption Points

### 2016-08-08 oopsla-16/evaluation.tex
change formatting according to camready author package

\subsection{\revision{Comparison to state-of-the-art MC}}%Comparing Iterative Deepening to SSS-MC
\label{sec:eval-sssmc}

@@

\subsection{Comparing to single-pass data-race analysis}
\label{sec:eval-dr}
% Though we mechanically verify whether each data race candidate leads to a bug, each new PP can increase combinatorially..... obviously wish to avoid...

>>>>

\subsection{\revision{Comparison to State-of-the-Art MC}}%Comparing Iterative Deepening to SSS-MC
\label{sec:eval-sssmc}

@@

\subsection{Comparing to Single-Pass Data-Race Analysis}
\label{sec:eval-dr}
% Though we mechanically verify whether each data race candidate leads to a bug, each new PP can increase combinatorially..... obviously wish to avoid...

### 2016-08-08 oopsla-16/paper.tex
Incorporate pure HB graphs and discussion in evaluation section; tons of prose changes omg
fix line break in conclusion
prepare for cam ready revisions
change formatting according to camready author package

\documentclass[10pt,times,numbers]{sigplanconf}
\usepackage[2ndsubmission]{oopsla2016}

@@

\usepackage{amsmath}
\usepackage{url}
\usepackage{enumitem}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{amsthm}
\usepackage[colorlinks=true,allcolors=blue,breaklinks,draft=false]{hyperref}
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}

@@

\newcommand\revision[1]{#1}
\definecolor{purple}{RGB}{192,0,192}
\newcommand\revisionx[1]{\hilight{purple}{#1}\xspace}
%\newcommand\revision[1]{\hilight{purple}{#1}}

@@

\authorinfo{Ben Blum}{Carnegie Mellon University}{bblum@cs.cmu.edu}
\authorinfo{Garth Gibson}{Carnegie Mellon University}{garth@cs.cmu.edu}
%\authorinfo{\vspace{24pt}}{}{}

@@

\revision{We present \quicksand, a new stateless model checking framework}~which
manages the exploration of many state spaces using different preemption points.
It uses state space estimation to prioritize jobs most likely to complete in a fixed CPU budget,
and it incorporates data-race analysis to add new preemption points on the fly.
Preempting threads during a data race's instructions
%These preemption points allow us to check whether each data-race can produce an observable failure, and
can automatically classify the race as buggy or benign,
and uncovers new bugs not reachable by prior model checkers.
%
It also enables full verification of all possible schedules when every data race is verified as benign within the CPU budget.
In our evaluation, \quicksand~found
%with data-race preemption points
1.5x as many bugs and verified 4.3x as many tests compared to \revision{prior model checking approaches}. %stateless model checking without data-race preemption points.
%Our evaluation shows this technique is
%more effective than single-state-space model checking
%%both at finding more bugs and at completing more state spaces when no bug exists.
%both at finding the same bugs faster and at finding new bugs entirely.
\end{abstract}

\revision{\category{D.2.4}{Software Engineering}{Software/Program Verification}}
%\category{D.2.5}{Software Engineering}{Testing and Debugging}
%
%% general terms are not compulsory anymore,
%% you may leave them out
%\terms
%term1, term2
%
%\keywords
%keyword1, keyword2

@@

\url{https://github.com/bblum/oopsla-quicksand}
% TODO CAMREADY: Make data set, at least, public.
\url{https://github.com/bblum/oopsla-dataset}

>>>>

\documentclass[10pt,times,numbers]{sigplanconf}
\usepackage[final]{oopsla2016}

@@

\usepackage{amsmath}
\usepackage{url}
\usepackage{enumitem}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{xspace}
\usepackage{amsthm}
\usepackage{flushend}
\usepackage{color}
\usepackage[colorlinks=false,breaklinks,draft=false]{hyperref}
\newcommand{\doi}[1]{doi:~\href{http://dx.doi.org/#1}{\Hurl{#1}}}

@@

% presubmit revisions
\newcommand\revision[1]{#1}
\definecolor{purple}{RGB}{192,0,192}
%\newcommand\revision[1]{\hilight{purple}{#1}}
% 2nd round revisions
%\newcommand\revisionx[1]{\hilight{purple}{#1}\xspace}
\newcommand\revisionx[1]{#1}
% cam ready revisions
\newcommand\revisionz[1]{\hilight{purple}{#1}\xspace}

@@

\authorinfo{Ben Blum}{Carnegie Mellon University, USA}{bblum@cs.cmu.edu}
\authorinfo{Garth Gibson}{Carnegie Mellon University, USA}{garth@cs.cmu.edu}
%\authorinfo{\vspace{24pt}}{}{}

@@

\revision{We present \quicksand, a new stateless model checking framework}~which
manages the exploration of many state spaces using different preemption points.
It uses state space estimation to prioritize jobs most likely to complete in a fixed CPU budget,
and it incorporates data-race analysis to add new preemption points on the fly.
Preempting threads during a data race's instructions
%These preemption points allow us to check whether each data-race can produce an observable failure, and
can automatically classify the race as buggy or benign,
and uncovers new bugs not reachable by prior model checkers.
%
It also enables full verification of all possible schedules when every data race is verified as benign within the CPU budget.
In our evaluation, \quicksand~found
%with data-race preemption points
\revisionx{1.25x} as many bugs and verified 4.3x as many tests compared to \revision{prior model checking approaches}. %stateless model checking without data-race preemption points.
%Our evaluation shows this technique is
%more effective than single-state-space model checking
%%both at finding more bugs and at completing more state spaces when no bug exists.
%both at finding the same bugs faster and at finding new bugs entirely.
\end{abstract}

\revision{\category{D.2.4}{Software Engineering}{Software/Program Verification}}
\keywords{model checking, data races, verification}
%\category{D.2.5}{Software Engineering}{Testing and Debugging}
%
%% general terms are not compulsory anymore,
%% you may leave them out
%\terms
%term1, term2
%
%\keywords
%keyword1, keyword2

@@

\url{https://github.com/bblum/oopsla-quicksand}

% TODO CAMREADY: Make data set, at least, public.
\url{https://github.com/bblum/oopsla-dataset}
